---
title       : Slidify
subtitle    : First project
author      : raicadaudinh
job         : khong nghe nghiep
framework   : revealjs       # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---.class #id1 bg:yellow

## Intercountry Life-Cycle Savings Data

Data on the savings ratio 1960-1970.
A data frame with 50 observations on 5 variables.

1.         sr    aggregate personal savings </br>
2.	 pop15	 % of population under 15 </br>
3.	 pop75	 % of population over 75 </br>
4.	 dpi	 real per-capita disposable income </br>
5.	 ddpi	 % growth rate of dpi </br>


_source_ "Sterling, Arnie (1977) Unpublished BS Thesis. Massachusetts Institute of Technology."" </br>
"Belsley, D. A., Kuh. E. and Welsch, R. E. (1980) Regression Diagnostics. New York: Wiley."" 

--- .class #id1 bg:yellow 

## Data
```{r, echo=TRUE}
library(datasets)
data(LifeCycleSavings)
head(LifeCycleSavings)

```










---
## Exploring data
We can not conclude anything from the plot
```{r, echo=TRUE}
pairs(~.,data=LifeCycleSavings, 
   main="Correlation matrix")
```













---
## Regression model

```{r, echo=TRUE}
fit<- lm(sr~., data=LifeCycleSavings)
summary(fit)$coefficients

```











---
## Which variable coefficient's are significantly different from 0?



<br/>
-pop15 and ddpi
</br>
-explanation Pr(>|t|)<<0.5%



